# The `sixs` package

## Purpose

The `sixs` package automates obtaining atmospheric correction parameters from by programmatically filling up the [web interface](https://www-loa.univ-lille1.fr/Wsixs/) with user-provided inputs.

## Setup

### Installing the package

Package `sixs` can be installed from GitHub as follows:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("michaeldorman/sixs")
```

### Setting up a Selenium server

#### Overview

Running the `sixs_params` function, to get the 6S parameters, requires a Selenium server. The server connection needs to be passed as a parameter named `remote_driver` to the `sixs_params` function. 

The recommended way to run a Selenium server is through docker. Detailed instructions on how to do that can be found in the [Docker vignette](https://cran.r-project.org/web/packages/RSelenium/vignettes/docker.html) of package `RSelenium`.

#### Local server

You can start your own local server, for example using the following expression on the command line (Ubuntu 18.04):

```sh
docker run -d -p 4445:4444 selenium/standalone-firefox:2.53.1
```

then connecting to the server from R to create the `remote_driver` object:

```{r, eval=FALSE}
library(RSelenium)
remote_driver = remoteDriver(remoteServerAddr = "localhost", port = 4445L)
remote_driver$open(silent = TRUE)
```

#### Demo server

Alternatively, you can use the demo server we set up for demontrating the package. Here is a small example where we browse to google.com and print the page title:

```{r}
library(RSelenium)

# Remote driver
remote_driver = remoteDriver(remoteServerAddr = "164.90.191.95", port = 4445L)

# Open
remote_driver$open(silent = TRUE)

# Browse to google.com & print page title
remote_driver$navigate("https://www.google.com")
remote_driver$getTitle()

# Close
remote_driver$close()
```

Note that the connection needs to be closed at the end using:

```{r, eval=FALSE}
remote_driver$close()
```

Keeping the connection open consumes RAM and eventually can make the server crash! The demo server is restarted automatically every day at 4AM. If you encounter a problem, please open an [issue](https://github.com/michaeldorman/sixs/issues).

## Example

### Overview

The following sections demonstrate the entire process of going from a raw Venus satellite image to an atmospherically-corrected reflectance image. 

### Input data

The input data includes:

1. The Venus satellite image (`venus1`)
1. The Venus satellite image metadata (`venus1m`)
1. Venus bands metadata (`bands`)

The image:

```{r}
library(sixs)
venus1
```

```{r}
plot(venus1)
```

Metadata:

```{r}
substr(venus1m, 1, 80)
```

Venus bands metadata:

```{r}
bands
```

### Getting image metadata

Metadata from `HDR` file:

```{r}
library(XML)
l = xmlToList(venus1m)
m = get_venus_metadata(l, band = 1)
m
```

General metadata on Venus bands.

### Reflectance to radiance

Venus satellite images are provided in TOA reflectance values multiplied by 1000. However, the 6S algorithm requires the imput to be TOA radiance values. 

Therefore, to proceed the image values need to be divided by 1000:

```{r}
venus1 = venus1 * 0.001
```

In the example, we atmospherically correct a specific band (3), therefore we also subset the third layer from the `venus1` image:

```{r}
venus1 = venus1[,,,3,drop=TRUE]
names(venus1) = "TOA reflectance"
```

Here what the TOA reflectance values in band 3 of the `venus1` sample image look like:

```{r}
plot(venus1)
```

Then, the resulting TOA reflectance values need to be converted back to TOA radiance values. This can be done using function `refl_to_rad`. 

Here is an example of converting the band 3 of the `venus1` image from TOA reflectance to TOA radiance:

```{r}
m = get_venus_metadata(l, band = 3)
venus1_toa_rad = refl_to_rad(
  toa_refl = venus1,
  date = m$date,
  esun = bands$esun[3],
  solar_zenith_angle = m$solar_zenith_angle
)
names(venus1_toa_rad) = "Band 3, TOA radiance"
```

```{r}
plot(venus1_toa_rad)
```

When the satellite image is given in radiance units, the inverse `rad_to_refl` function can be used to convert it to a TOA reflectance image. The required data includes the `date`, `esun` and `solar_zenith_angle`, same as in `refl_to_rad`. 

### Atmospheric parameters from Aeronet

The 6S algorithm requires obtaining three meteorological parameters from the AERONET stations data, namely:

* AOD550nm
* Uw [g cm-2]
* UO3 [cm/atm]

Here is how to obtain these parameters:

* Navigate to the AERONET [web page](https://aeronet.gsfc.nasa.gov/cgi-bin/draw_map_display_aod_v3) to open the available data from AERONET stations worldwide.

* Choose an AEORONET station that is geographically located near your site. It is possible to click on the map several times in order to zoom in and choose the relevant station easily. For example in Figure 1 below is a list of AERONET stations in the western Middle East (Israel, Egypt, Cyprus and Greece).

Figure 1: Example of a list of AERONET stations. 

* Click on the relevant station. This will open a window as shown in Figure 2.

* Choose the relevant period (year) on the left panel. In case the user does not choose the relevant period, the website will return data for the current year as a default. Another option is to choose a specific relevant day on the right panel; however, it this is not useful for atmospheric correction of satellite imagery since these corrections require a daily temporal resolution and not hourly.

* Click on AOD Level 1.0 to download the data. 

Figure 2: A window of meteorological data for Sede Boker site in Israel. The links for downloading the relevant data are shown in red squares. 

* Accept the data usage agreement in the window shown in Figure 3:
    
Figure 3: Acceptation of AERONET data usage.

* Download and unzip the data (a `.lev1` file) and open the data in Excel using the option 'from text' in the 'data' tab.

* Calculate the AOD in 550 nm: use the AOD in 675 nm (AOD_675nm column) and AOD in 500 nm (AOD_500nm column) in the formula below to calculate AOD in 550 nm:

* Find the perceptible water value under the column 'Precipitable_Water(cm)' that presents the water vapor (Uw) in [g cm-2].

* Find the Ozone concentration value under the column 'Ozone(Dobson)' that presents the O3 concentration in Dobson units. Multiply this value by 0.001 to obtain the Ozone concentration in [cm/atm].

Specifically for `venus1`, the required variables are:

```{r}
Uw = 0.665071
Uo3 = 0.2982371
opticalDepth = 0.1105934
```

### Additional parameters

`GroundCondition` is usually `"Patchy Ground"`.

`TargetReflectance` depends on what the project focuses on.

`EnvironmentReflectance` depends on surrounding cover.

`TargetRadius` needs to be smaller than pixel size, in meters (for Venus <5.3)

```{r}
GroundCondition = "Patchy Ground"
TargetReflectance = "Vegetation"
EnvironmentReflectance = "Vegetation" 
TargetRadius = 0.5
```

### 6S parameters

Once the server is set and the `remote_driver` object exists, you can execute the `sixs_params` function to get the 6S parameters. 

For example, for band 3 from the `venus1` image:

```{r}
remote_driver$open(silent = TRUE)
xcoefficients = sixs_params(
  remote_driver = remote_driver, 
  day = as.numeric(format(m$date, "%d")),
  month = as.numeric(format(m$date, "%m")), 
  SolarZenithalAngle = m$solar_zenith_angle, 
  SolarAzimuthalAngle = m$solar_azimuth_angle,
  ViewZenithalAngle = m$view_zenith_angle,
  ViewAzimuthalAngle = m$view_azimuth_angle, 
  Longitude = m$longitude, 
  Latitude = m$latitude, 
  Uw = 0.665071, 
  Uo3 = 0.2982371, 
  opticalDepth = 0.1105934, 
  LowerWavelength = bands$lower[3], 
  UpperWavelength = bands$upper[3],
  TargetAltitude = m$elevation,
  GroundCondition = "Patchy Ground",
  TargetReflectance = "Vegetation",
  EnvironmentReflectance = "Vegetation", 
  TargetRadius = 0.5,
)
remote_driver$close()
```

You can use the `.screenshot=TRUE` parameter in the above function call for viewing the web interface throughout the process. This will create a temporary file named `rselenium_screenshot.png` in the current working directory.

The result is a named numeric vector with the 6S parameter values:

```{r}
xcoefficients
```

### TOA to BOA

Finally, using the 6S parameters we can conver the TOA radiance image to a BOA reflectance image, using function `toa_to_boa`:

```{r}
venus1_boa_refl = toa_to_boa(
  toa_rad = venus1_toa_rad, 
  params = xcoefficients
)
names(venus1_boa_refl) = "Band 3, BOA reflectance"
```

Here is the result:

```{r}
plot(venus1_boa_refl)
```

Done!
