---
title: "Processing multiple images"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multiple images}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.align = "center", 
  fig.width = 6, 
  fig.height = 4
)
```

## Overview

This tutorial contains a reproducible example of correcting 5 Venus satellite images.

## Download sample data

First we will download a table with the images list and external metadata, such as atmospheric parameters obtained from AERONET (see [first vegnette](intro.html) for details).

```{r}
dat = read.csv("http://164.90.191.95:8000/metadata.csv")
```

```{r}
dat
```

Next we download the sample images and their respective metadata files. Each image is a 15-band Venus satellite image. The first 12 bands, which we are going to use, contain TOA reflectance values multiplied by 1000.


A temporary directory can be created for this purpose:

```{r, eval=FALSE}
dir = tempdir()
```

Aletrantively, we can specify a specific location:

```{r}
dir = "~/Downloads/venus"
```

Now, we download the images to the specified directory:

```{r, eval=FALSE}
options(timeout = 600)

# Download images
files = paste0(gsub("_L1VALD_", "_PDTIMG_L1VALD_", dat$id), ".DBL.tif")
files
url = paste0("http://164.90.191.95:8000/", files)
for(i in url) download.file(i, file.path(dir, basename(i)))

# Download metadata
files = paste0(dat$id, ".HDR")
files
url = paste0("http://164.90.191.95:8000/", files)
for(i in url) download.file(i, file.path(dir, basename(i)))
```

Here is the raw first image:

```{r}
library(stars)
in_file = paste0(gsub("_L1VALD_", "_PDTIMG_L1VALD_", dat$id[1]), ".DBL.tif")
r = read_stars(file.path(dir, in_file))
r = r[,,,1:12]
plot(r, breaks = "equal")
```

## Atmospheric correction

Next, we are going to process the images, calculating five atmospherically-corrected 12-band new images:

```{r}
library(sixs)
library(RSelenium)
library(XML)

for(image in dat$id) {

  # Read image
  in_file = paste0(gsub("_L1VALD_", "_PDTIMG_L1VALD_", image), ".DBL.tif")
  r = read_stars(file.path(dir, in_file))
  
  # Subset bands
  r = r[,,,1:12]

  # Normalize
  r = r * 0.001

  # Empty list to keep results
  output = list()
  for(i in 1:12) {

    # Subset band
    s = r[,,,i,drop=TRUE]

    # Read metadata
    input_m = paste0(image, ".HDR")
    l = xmlParse(file.path(dir, input_m))
    l = xmlToList(l)
    m = get_venus_metadata(l, band = i)

    # TOA refl -> TOA rad
    s = refl_to_rad(
      toa_refl = s,
      date = m$date,
      esun = bands$esun[i],
      solar_zenith_angle = m$solar_zenith_angle
    )

    # 6S coefficients
    remote_driver = remoteDriver(remoteServerAddr = "164.90.191.95", port = 4445L)
    remote_driver$open(silent = TRUE)
    xcoefficients = sixs_params(
      remote_driver = remote_driver, 
      day = as.numeric(format(m$date, "%d")),
      month = as.numeric(format(m$date, "%m")), 
      SolarZenithalAngle = m$solar_zenith_angle, 
      SolarAzimuthalAngle = m$solar_azimuth_angle,
      ViewZenithalAngle = m$view_zenith_angle,
      ViewAzimuthalAngle = m$view_azimuth_angle, 
      Longitude = m$longitude, 
      Latitude = m$latitude, 
      Uw = dat$uw_g_cm2[dat$id == image], 
      Uo3 = dat$uo3_cm_atm[dat$id == image], 
      opticalDepth = dat$optical_depth_550nm[dat$id == image], 
      LowerWavelength = bands$lower[i], 
      UpperWavelength = bands$upper[i],
      TargetAltitude = m$elevation,
      GroundCondition = "Patchy Ground",
      TargetReflectance = "Vegetation",
      EnvironmentReflectance = "Vegetation", 
      TargetRadius = 0.5,
      quiet = TRUE
    )
    remote_driver$close()

    # TOA rad -> BOA refl
    s = toa_rad_to_boa_refl(s, xcoefficients)

    # Add result to list
    output[[i]] = s

  }

  # Combine to multi-band raster
  output$along = 3
  output = do.call(c, output)
  
  # Write
  out_file = gsub(".tif", "_out.tif", in_file, fixed = TRUE)
  write_stars(output, file.path(dir, out_file))

}
```

Here is the corrected first image:

```{r}
s = read_stars(file.path(dir, out_file))
plot(s, breaks = "equal")
```

